\plaintitle

### 2020-03-14 wip-design/paper.tex
Case study evaluation

\documentclass{sigchi}
\usepackage{xspace}
\usepackage{fancyvrb}
\usepackage{inconsolata}
\usepackage{xcolor}

@@

We argue that iterative prompting is easier than other forms of interaction, because it
follows the \emph{recognition over recall} usability heuristic. The users are only required to
choose from an offered list of options, rather than having to recall a possible command
(to type in a command line) or a syntax in a text-based programming environment.

@@

this is between-user user study

FIRST: How one area transfers to another?

DEMO: WorldBank
explain everything

DISPLAY: Public order and safety, Defence
\begin{verbatim}
expenditure.byService.'Public order and safety'.inTermsOf.GDP
expenditure.byService.Defence.inTermsOf.GDP
\end{verbatim}

DEMO: Graph DB
explain everything

\begin{verbatim}
drWho.Character.Doctor.'ENEMY_OF'.'[any]'
  .'APPEARED_IN'.'[any]'.'explore_properties'.explore
  .'group data'.'by 1-name'.'count distinct 2-title'
\end{verbatim}

DISPLAY: Who has larges travel expenses?
(and in London only?)

\begin{verbatim}
lords.'sort data'.'by Travel Costs descending'

lords
  .'filter data'.'County is'.London.then
  .'sort data'.'by Travel Costs descending'
\end{verbatim}

SECOND: No experts are needed

DEMO: explain how live preview works, explain how '.' works,
explain how newlines and indentation work

DISPLAY 'CO2 emissions (metric tons per capita)'

\begin{verbatim}
worldbank.byCountry.'United Kingdom'
  .'Economy & Growth'.'GDP per capita (current US$)'

worldbank.byCountry.Germany
  .'Economy & Growth'.'GDP per capita (current US$)'

worldbank.byCountry.'Czech Republic'
  .'Economy & Growth'.'GDP per capita (current US$)'
\end{verbatim}

DISPLAY: Top athletes from London

\begin{verbatim}
olympics
  .'group data'.'by Team'.'sum Gold'.then
  .'sort data'.'by Gold descending'.then
  .paging.take(5)
  .'get series'.'with key Team'.'and value Gold'
\end{verbatim}

THIRD: 'then'

DEMO: Show worldbank
GIVE: Commented source code using 'olympics'
DISPLAY: Top athletes from London (think-aloud)

QUESTIONS

1) Did I tell you enough in the introduction to get started?

Say we want to provide educational materials for journalists
(with limited budgets), what would be the most important?

2) Video or just code samples?

We'll have more data sources than we can write tutorials for

3) Do we just teach them how the environment works?

4) What do we need to teach about a data source?

"i haven't done 'then' "

USABILITY ISSUES
- need to delete the rest of the line
- when you leave ".c" there, things break
- typing . without indentation does not work
- purple box vs. black wrench icons in the completion
- how do you know top level data sources
- 'games is' bit (with the year) - methods suck!

>>>>

\documentclass{sigchi}
\usepackage{xspace}
\usepackage{fancyvrb}
\usepackage{inconsolata}
\usepackage{xcolor}
\usepackage{tikz}
\newcommand*{\priority}[1]{\begin{tikzpicture}[scale=0.12]%
    \draw (0,0) circle (1);
    \fill[fill opacity=1,fill=black] (0,0) -- (90:1) arc (90:90-#1*3.6:1) -- cycle;
    \end{tikzpicture}}

@@

%https://www.nngroup.com/articles/recognition-and-recall/
We argue that iterative prompting is easier than other forms of interaction, because it
follows the \emph{recognition over recall} usability heuristic. The users are only required to
choose from an offered list of options, rather than having to recall a possible command
(to type in a command line) or a syntax in a text-based programming environment.

@@

business team of a non-profit research organization, including a former journalist

\subsection{Research questions}

\paragraph{RQ1: Can end users explore data with The Gamma?}

\paragraph{RQ2: Can knowledge transfer between data sources?}

\paragraph{RQ3: Can users learn from just code samples?}

\subsection{Study design}
this is between-user user study

\subsection{Results}
it is good

\paragraph{Can end users explore data with The Gamma?}
Yes, the table shows the results.
People who spent between 10 and 25 minutes (average 18 minutes) working with The Gamma
Out of 13 people, all completed some work, 1 person completed partly and 6 were able
  to complete the task with small assistance (related to methods and syntax, as discussed below)

\begin{quote}
\emph{``This is actually pretty simple to use. You think about the logic of what you're actually asking and
    then you try to get it into the format you can. But knowing where it comes from would tell you how
    to trust it.''}
\end{quote}

we should use it as a training resource for students - would students get this?

\begin{quote}
\emph{``I don't think they'd need more than 5 minute video. This is a data
  source, this is what's in there.''}
\end{quote}

\begin{quote}
\emph{``for somebody who does not do coding or programming, this does not feel that daunting. it's not like you're giving me large screen full of code, which is reassurring" (~36)''}
\end{quote}

\paragraph{RQ2: Can knowledge transfer between data sources?}
expenditure task (#1-#5) and lords task (#9-#11) - is transfer from worldbank to expenditure and
from graph data to lords; the former transfers more directly, the latter less so (mainly because
of then and methods, which we discuss below)

\begin{quote}
  \emph{``I found it quite easy to translate what you showed us in the demo to the new dataset, i though it was quite easy to just get how that works''}
\end{quote}

\paragraph{RQ3: Can users learn from just code samples?}
in the worldbank task (#6-#9), users were given just a code sample and demo using no real
data source. They were able to complete based on just following and modifying code sample (to find other data).
(no problems they had were related to data source)

- "a video would just be this [code samples] anyway" (~19)
- "keystroke by keystroke video would be good"

\begin{quote}
  \emph{``I think providing one video of one example is good and maybe a couple of little examples of code wher people can see the kind of things you can do" (28:02)''}
\end{quote}

"more than one example of code would be useful because I'd be less confused about options"

\subsection{Further observations}

\paragraph{Making complex things possible hurts}
#11, #12, #13 all struggled with methods (they show in the completion lists)

\paragraph{Benefits and drawbacks of text}

AG - confused by indentation (Monaco inserts it automatically - duh!)
it does not work if you have it and add a new to-level thing;

BM uses copy & paste to copy thing and replace one identifier in the middle
(which would be difficult to do with non-textual representation)

people occasionally miss '.' when typing and try to use a space

\paragraph{How users understand the then keyword}

what is then: "allows us to chain together the operations"
is it special? "maybe I need it just to split over multiple lines" (experiments..) "no!"

"when you explained about the "dot then" that was a really useful thing to know. When I found that, I was like 'this is fine, this is doable'. If I knew this from the start, it would [have been easier]" (~27)

"I thought 'then' starts a new line. (...) I realised there was no 'then' after the 'paging' command. "
"It starts a new line or a new query? I assumed there would be one after 'paging' too."

\subsection{Conclusions}
(former journalist)
Do you think this is something journalists could figure out how to use?
"Yeah, I think so. There's a lot of effort going into data journalism that programming could make much quicker,
but I was always nervous about code." ... "Something like this would really simplify things."

\begin{table}
  \centering
  \begin{tabular}{l l l c l}
    \toprule
      & {\small \textit{Task}}
      & {\small \textit{Kind}} & {\small \textit{Completed}}
      & {\small \textit{Notes}} \\
    \midrule
    \small \#1 & \small expenditure & \small cube & \priority{50} & {\small Obtained one of two data series}\\
    \small \#2 & \small expenditure & \small cube & \priority{100} & {\small Explored furhter data series }\\
    \small \#3 & \small expenditure & \small cube & \priority{100}& {\small Explored further data series }\\
    \small \#4 & \small expenditure & \small cube & \priority{75}& {\small With hint to use another member }\\
    \small \#5 & \small expenditure & \small cube & \priority{100}& {\small Explored further data series }\\
    \small \#6 & \small worldbank & \small cube & \priority{75} & {\small With general syntax hint }\\
    \small \#7 & \small worldbank & \small cube & \priority{100} & {\small Completed very quickly }\\
    \small \#8 & \small worldbank & \small cube & \priority{100} & {\small Extra time to find data }\\
    \small \#9 & \small lords & \small table & \priority{75} & {\small  Struggled with composition}\\
    \small \#10 & \small lords & \small table & \priority{100} & {\small Completed very quickly }\\
    \small \#11 & \small lords & \small table & \priority{75} & {\small With a hint to avoid methods}\\
    \small \#12 & \small olympics & \small table & \priority{75}  & {\small With a hint to avoid methods}\\
    \small \#13 & \small olympics & \small table & \priority{75}  & {\small With a hint to avoid methods}\\
    \bottomrule
  \end{tabular}
  \caption{Table captions should be placed below the table. We
    recommend table lines be 1 point, 25\% black. Minimize use of
    table grid lines.}~\label{tab:table1}
\end{table}
